Motmot: A Distributed Chat Protocol

### 2012-05-05 paper/paper.tex
Finishing paper

  \item[Reconnection:]

@@

    We implement an out-of-band sync-and-truncate protocol, which is used by
    the proposer to issue consistent system-wide deletion of old commits.  A
    proposer asks all protocol participants to return the last contiguous
    commit which their respective clients have learned about.  Once it receives
    a response from \emph{all} participants, it can take the minimum instance
    number of those commits and safely command all participants to truncate
    up to that point.

  \item[Connection continuations:]
\end{description}

@@

\section{Acknowledgments}

>>>>

  \item[Redirection:]
    In the presence of connection failures, protocol participants may at times
    have an incorrect notion of who the designated proposer is.  In particular,
    we have the following three cases:
    \begin{enumerate}
      \item A participant thinks it is the proposer and tries to prepare, but
        a majority of participants are still connected to the true proposer.
      \item A proposer thinks that a participant has been disconnected from
        the system, but a majority of participants are still connected to it.
      \item A participant issues a request to another participant who it
        incorrectly identifies as the proposer.
    \end{enumerate}
    To deal with the former two cases, we implement a majority rejection
    mechanism for prepares and part decrees.  When a majority rejects a
    prepare, they indicate their identification of the true proposer.
    The preparer, who belives himself to be the proposer, then attempts
    to reconnect to this true proposer.  Similarly, rejections of part
    induce the issuer of the decree to attempt reconnection to the target
    of the part.

    If participants misidentify the proposer when making a request, the
    individual that they identified as the proposer will return the true
    identity of the proposer.  A single such response is enough to cause
    the requester to attempt reconnection.

@@

    We implement an out-of-band sync-and-truncate protocol, which is used by
    the proposer to issue consistent system-wide deletion of old commits.  A
    proposer asks all protocol participants to return the last contiguous
    commit which their respective clients have learned about.  Once it receives
    a response from \emph{all} participants, it can take the minimum instance
    number of those commits and safely command all participants to truncate
    up to that point.
\end{description}

@@
